Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-17 report/report.tex
Add virtual city image

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_map_residential_footpath_compare}
    \caption{Example segments of the Stockholm metropolitan area with highlighted residential streets (left) and footpaths (right). Here can be seen the unique character of footpaths. Walkways in parks appear to grow much more organically, and pavements form rough grid systems with organic branches that bridge over city blocks.}
    \label{fig:osm-slu-map}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_virtual_city}
    \caption{Real-world cities are complex collections of buildings, blocks and road networks that interconnect them all. Creating 3D virtual cities using methods of procedual generation is an emerging research field that comes with its own set of challenges.}
    \label{fig:virtual-city}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_map_residential_footpath_compare}
    \caption{Example segments of the Stockholm metropolitan area with highlighted residential streets (left) and footpaths (right). Here can be seen the unique character of footpaths. Walkways in parks appear to grow much more organically, and pavements form rough grid systems with organic branches that bridge over city blocks.}
    \label{fig:residential-footpath-map}
\end{figure}
